---
title       : Medicaid Inpatient Disease Rate Distribution for Pediatric Hospital Discharges by Zip Code 
subtitle    : for year 2011 - 2012
author      : Jiayu Huang
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}

--- 

## Goal? What for?

Present the observed rate (per 100,000 people) for medicaid inpatient discharges of 7 Pediatrics disease types from 2011 to 2012 in New York state


---

## What you can do ?

  * select an input year from 2011 - 2012  
  
  * select a type of disease (7 in total) 
  
  * select area in NY state by zipcode 
  

---

## What I can offer?

1. Given a zip code, show the city and the county the zip code is in.

2. Given a year in 2011-2012 and a type of disease, show the geographical distribution of observed disease rate in NY and the Medicaid population of different zipcodes. 

3. Given a type of disease and a zipcode in NY state, show the barplot of (average) observed disease rates of the zipcode area,  the county which the zipcode is in and the whole state in 2011-2012.

4. Given a type of disease and a zipcode in NY state, show the boxplot of state-wide average observed disease rates.



---

## An example 
```{r, echo = F, eval = T}
load("cleaned_dat.rdata")
```
```{r, fig.height = 6, fig.align='center'}
ad <- subset(cleaned_dat, disease == "Asthma" )
boxplot(ad$obs_rate~ad$year,horizontal = TRUE, xlab = "Observed rate", 
        main = "State-wide Observed rate for Asthma by Year")  

```
---





